Foremost, I would like to express my sincere gratitude to my advisors Prof. Parag Singla and Prof. Rohan Paul for the continuous support of my Master's study and research, for their patience, motivation, enthusiasm, and immense knowledge. Their guidance helped me in all the time of research and writing of this thesis. I thank them for maintaining a very understanding and enjoyable research culture, and always motivating us to put in our best efforts, even working with us at odd hours whenever needed. I could not have imagined having a better pair of advisors and mentors for my Master's study.

I would also like to thank fellow IIT Delhi students: Arnav Tuli, Namasivayam K and Himanshu Gaurav Singh, for being the best team-mates I could have asked for. All of my Master's research have been carried out with the help of their continuous support and efforts. I will cherish our late-night sprints during our paper submissions and our stimulating discussions regarding minute details of our work. I will always remember the sincerity and amazing work ethic that each of them have taught me.

I extend gratitude to the support my advisors recieved for our work: DARPA Explainable AI (XAI)
Program, IBM AI Horizon Networks (AIHN) grant, IBM SUR awards, the Pankaj Gupta
Young Faculty Fellowship, and the CSE Research Acceleration fund of IIT Delhi. I thank the IIT Delhi HPC facility for computational resources.

Last but not the least, I would like to thank my family: my parents and my sister for always supporting and motivating me throughout my life, and being my pillars of strength. They have taught me to always put my best effort in all my endevours and have consistently set this example for me to follow. I am grateful to them for cultivating my curiousity and pushing me to be a good human being along my journey.